\documentclass[10pt]{beamer}
\usepackage[utf8]{inputenc}
\title{Perl \\ Post Install Tests}

\begin{document}

\begin{frame}
\titlepage
\end{frame}


\begin{frame}[fragile]
\frametitle{Upgrading dependencies w/fear}
\begin{enumerate}
  \item Install distribution containing a module named \verb|Bear|
  \item Install distribution containing module \verb|Human|, which depends on the availability of \verb|Bear|'s \verb|ride()| method
  \item (time passes...)
  \item Upgrade to a newer distribution version of \verb|Bear|, which does NOT have the \verb|ride()| method; The author of \verb|Bear| heard it's not safe to ride bears.
  \item {\bf *BOOM*} \verb|Human|'s attempt to \verb|ride()| fails!
  \item \verb|Human| gets eaten by \verb|Bear| and/or customer.
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Sources of \emph{upgrade fear}}
\begin{itemize}
  \item Don't assume CPAN authors have a commitment to their APIs. They may change at any time - even if the CPAN/Perl community has a history of preserving backwards compatibility!
  \item No \emph{trivial} way of verifying if the installed Perl/CPAN dists still work.
  \item Modules might be used in ways unintended by the author.
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Detecting breakage}
We want to detect the upgrade bug/bear early to avoid getting eaten! Our options are:
\begin{itemize}
\item Run your code and see if something breaks
\item Run your code's integration/smoke tests
\item Check cpantesters.org
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{We want more options!}
\begin{itemize}
\item Run tests for all modules/distributions found in \verb|@INC|
\item Run tests for the dists that depend on the one you're about to upgrade
\item Run tests in any system environment (development, test/CI, staging and if necessary, {\bf production})
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Post Install Test requirements}
\begin{itemize}
\item The tests for the installed modules must be available (installed).
\item It must be possible to locate tests for a specific distribution and version.
\item Distribution dependencies are saved and installed.
\item It must be possible to do determine a distribution's reverse dependencies, so we can only run the tests that are affected by a specific dist upgrade.
\item Writing a \emph{best practices} guide on how to make tests that can be used post-install.
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Demo - Module::Build::PIT}
\begin{itemize}
\item Extension of \verb|Module::Build|.
\item Environment variable \verb|PERL_INSTALL_TESTS| controls if tests should be installed when using  \verb|./Build install| (Also possible to use \verb|./Build installtests| for the same effect w/o ENV).
\item Tests are installed under \verb|$install_base/auto/tests/$distname-$distversion/|.
\item Test files are written to the \verb|.packlist| file.
\item Action \verb|testinc| uses the \verb|ExtUtils::Installed| distribution to retrieve the modules that would be loaded and their test files.
\item Action \verb|testrdeps| is a hack, and depends atm. on MetaCPAN for demonstration purposes.
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Future Work / Considerations}
\begin{itemize}
\item Permissions - Test that writes to devices, sockets(ports \textless \ 1024), t/... and more
\item Currently no trivial way of finding reverse dependencies locally
\item Integration with packaging systems
\item Upgrading \verb|test_requires| to regular \verb|requires|?
\item Best practices doc
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Code}
\begin{itemize}
\item Code and slides are on github!
\item \verb|https://github.com/bannaN/Module-Build-PIT|
\item \verb|https://github.com/bannaN/qa-hackathon-presentation|
\item Fork it now!
\end{itemize}
\end{frame}

\end{document}
